Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-09 icdm/submission/includes/related_work.tex
caching plus start intel describption

\subsection{Parellelization by the use of caching}
This idea was proposed by Vuurens et al. \cite{efficient}. The architecture used here is the SGM with a hierarchical softmax.

The general idea is to cache the most frequently used weight vectors, and update the model after a certain number of seen training samples, while taking in consideration the changes that happend during these number of seen training samples (the paper used the number 10). The unfrequent weight vectors are handled as in the original paper, i.e updated in shared memory after each training sample. This technique  allows it to avoid collosision for the most frequent words, and the author therefore hoped to be able to increase the number of concurrent threads.The general idea is to cache the most frequently used nodes of the binary tree used to memorize the probability distribution and update them on the shared single model after a certain number of seen words. The paper produced interesting results as they managed to decrease execution time by increasing the number of cores used for the calculation. This is very powerful because in the original implementation the execution time regressed after using more than 8 cores. It seems to indicate that too much overwriting was happening, as the number of concurrent threads surpasses a certain threshold. This can be seen in Figure \ref{fig:efficient}, where c31 is the model proposed by Vuurens et al.\cite{efficient}. The model did not suffer any accuracy loss in comparison to the original SGM model.
\begin{figure}[ht]
\centering
\includegraphics[scale=0.3]{images/cachingEfficiency.png}
\caption{Comparasion of the execution time in relation to the number of used cores \cite{efficient}}
\label{fig:efficient}
\end{figure}
This work proposes a very good way to parallelize the SGM, as in particular, it allows using more cores during the computation. As this approached focused on the Hierarchical softmax, in contrast to our work which used negative sampling, the next subsection covers optimizations of the Skip-Gram Model with negative sampling(SGNS).

\subsection{Parallization in shared and Distributed Memory}
In contrast to the above approach, this one, introduced by Ji et al. \cite{intel} focused on the Skip-Gram Model with negative sampling. The focus of this work was to reduce the cost of our vector to  vector multiplication in our loss funcion, see Equation \ref{eq:obj_neg_samples}, where the dot product of the word vector and the negative sampled as well as the context word is computed.
The main idea in this paper is to convert the level 1-BLAS (Basic Linear Subprogram) vector to vector operations to a level 3-BLAS matrix multiplication operation, which are efficiently implemented into hardware and consequently faster. To achieve such a transformation, Ji et al. decided to use the same negative samples for given amount of training samples. The training samples that will have the same negative samples are chosen as follows: given a word $w_c$ one can construct all the training samples where $w_c$ is a context word. This will result in the following training batch $X = \{({w_{in}}^i, w_c) | w_c~appears~in~the~context~of~{w_{in}}^i\}$. The matrix multiplication can be represented in the following way.
\[
\begin{bmatrix}
w_c \\
w_{n_1} \\
\vdots \\
w_{n_k}\\
\end{bmatrix}
*
\begin{bmatrix}
w_{in}^1\\
\vdots\\
{w_{in}}^{2m}\\
\end{bmatrix}
\]
where, $w_{n_1}...w_{n_k}$ are the shared negative samples. The above Matrix multiplication will compute the loss for each training sample and the weights of the used vectors will be updated after each batch. This method achieves a 3.6 fold increase in throughput, by only losing 1\% of accuracy. The presented results were achieved on CPU's, as many modern machine learning libraries make use of the parallelizing capabilities of GPU's for matrix multiplications, the next subsection covers the work done by Seulki and Youngmin \cite{gpu} that parellelized the SGNS on GPU's.

>>>>

\subsection{Parellelization by the use of caching}
This idea was proposed by Vuurens et al. \cite{efficient}. The architecture used here is the SGM with a hierarchical softmax. 
The general idea is to cache the most frequently used weight vectors, and update the model after a certain number of seen training samples, while taking in consideration the changes that happend during these number of seen training samples (the paper used the number 10). The unfrequent weight vectors are handled as in the original paper, i.e updated in shared memory after each training sample. This technique  allows it to avoid collosision for the most frequent words, and the author therefore hoped to be able to increase the number of concurrent threads. The paper produced interesting results as they managed to decrease execution time by increasing the number of cores used for the calculation. This is very powerful because in the original implementation the execution time regressed after using more than 8 cores. It seems to indicate that too much overwriting was happening, as the number of concurrent threads surpasses a certain threshold. This can be seen in Figure \ref{fig:efficient}, where c31 is the model proposed by Vuurens et al.\cite{efficient}. The model did not suffer any accuracy loss in comparison to the original SGM model.
\begin{figure}[ht]
\centering
\includegraphics[scale=0.3]{images/cachingEfficiency.png}
\caption{Comparasion of the execution time in relation to the number of used cores \cite{efficient}}
\label{fig:efficient}
\end{figure}
This work proposes a very good way to parallelize the SGM, as in particular, it allows using more cores during the computation. As this approached focused on the Hierarchical softmax, in contrast to our work which uses negative sampling, the next subsection covers optimizations of the Skip-Gram Model with negative sampling(SGNS).

\subsection{Parallization in shared and Distributed Memory}
In contrast to the above approach, this one, introduced by Ji et al. \cite{intel} focused on the SGNS. The focus of this work was to speed up the computation of the loss function of the SGNS described in Equation \ref{eq:obj_neg_samples}. Where the dot product of the center word  with negative samples as well as the context word is computed. The dot product is a level 1-BLAS operation and is not as efficiently implemented into hardware, as matrix multiplication which are a level 3-BLAS operation.  To achieve such a transformation, Ji et al. decided to use the same negative samples for given amount of training samples. The training samples that will have the same negative samples are chosen as follows: given a word $w_c$ one can construct all the training samples where $w_c$ is a context word. This will result in the following training batch $X = \{({w_{in}}^i, w_c) | w_c~appears~in~the~context~of~{w_{in}}^i\}$. The matrix multiplication can be represented in the following way.
\[
\begin{bmatrix}
w_c \\
w_{n_1} \\
\vdots \\
w_{n_k}\\
\end{bmatrix}
*
\begin{bmatrix}
w_{in}^1\\
\vdots\\
{w_{in}}^{2m}\\
\end{bmatrix}
\]
where, $w_{n_1}...w_{n_k}$ are the shared negative samples. The above Matrix multiplication will compute the loss for each training sample and the weights of the used vectors will be updated after each batch. This method achieves a 3.6 fold increase in throughput, by only losing 1\% of accuracy. The presented results were achieved on CPU's, as many modern machine learning libraries make use of the parallelizing capabilities of GPU's for matrix multiplications, the next subsection covers the work done by Seulki and Youngmin \cite{gpu} that parellelized the SGNS on GPU's.
